\chapter{Introduction}\label{C:intro}
This project seeks to design, implement, and evaluate an interactive 3D visualisation software system for displaying the content in the Kepler Exoplanets dataset. The deliverable is intended as a standalone 3D visualisation system with two modes of interaction of keyboard and mouse or Microsoft Xbox Kinect sensor. The resulting visualisation will convey the information in the dataset in a way that the target users, laypeople who have an interest in astronomy, can understand and interact with.

\section{Problem statement}
The complex nature of the data involved in this project causes a range of problems to arrise which this project attempts to address. The following subsections outline these in detail.
\subsection{Understanding the content in the dataset}
We often rely on visualisation when we solve problems. We create an image in our mind of a situation in order to make sense of it. http://nrich.maths.org/6447
\\\\
Understanding and analysing large datasets whose size defies simplistic or trivial analysis is a known issue that many areas of research are attempting to address, these areas of research range from data mining to visualisations to attempt to discover or highlight important aspects of the data so that people can more efficiently use it
\\\\
The content in the dataset used for this project is made up of records of each exoplanet discovered, each of which contains 46 fields. 

\subsection{Comprehension of planatery information}
Much of the information regarding planets is criptic and uninituitive, this make its understandability difficult. Visualisations in general attempt to address this issue by displaying information in a way that conveys the information in simplisitic ways that allows improved user comprehension.

\subsection{Exisiting solutions lack functionality}
Existing data visualisation techniques using this exoplanet dataset lack the ability to display sufficient detail on each exoplanet and do not provide answers to questions that can be answered by the Exoplanet attributes in the dataset. Existing solutions display only the size, temperature, and orbital information about the exoplanets. While this is useful information that informs users of important facts about the planets, it does leave a lot of potential information unseen and overlooked, for example, information about the type of planet, planets with similar traits, solar system information, similarity to earth and habitability. This project will therefore be focused on researching, implementing, and evaluating a new interactive visualisation system that will display additional information to users not included in previous visualisation systems.

\subsection{Effective user interaction with visualisation}
A visualisation that soley displays information without effective methods of interaction will not have the immersive qualities that keeps users engaged as would be the case with an interactive visualisation

\section{Key issues project addresses}
To summarise the above sections, this project addresses the following key issues:
\begin{enumerate}
 \item[I1.] Content in database form is difficult to view and understand.
 \item[I2.] Planetary information if complex and difficult to comprehend without a visual reference.
 \item[I3.] Exsiting visualisations for this dataset lack functionality.
 \item[I4.] User interaction is needed in a visualisation to make the most of the data displayed.
\end{enumerate}

\section{Contributions of this project}
This project will provide an extension of the Kepler Visualisation Tool \cite{kepler_github} that conveys more information and is easier for users to interact with than the original. This extension will be evaluated by a user experiment to ensure that it is successful in conveying the information contained in the dataset.
\\\\
The work and research completed for this project will allow for further improvement by other developers and researchers to extend and improve the visualisation created. This will provide further exposure of the Kepler dataset which will encourage learning about Exoplanets.
